### 2024-01-02 Scripts/Manuscript/manuscript.Rmd
changed the uses of the word thesis to either study or article, and added references to the github page were relevant.

abstract: |
  Recently, the influence of measurement related issues on replicability has received more investigations. 
  In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
  Building on this new line of research, this thesis assessed these influences in large scale replication projects. 
  Protocols from the Many Labs replication projects, and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures. Reliability did not relate to replicability, and was generally consistent between labs for each measure in the Many Labs projects. 
  The quality of measurement reporting in replication protocols did however relate to replicability.
  Additionally, tentative evidence was found for a relation between quality of measurement reporting in the protocol of a replication and the quality of measurement reporting in its related original study.
  Recommendations are given for researchers and replicators in order to improve measurement practices in replication, and ward its negative impact on replicability. 
  Additionally, directions are given for future research investigating the relationship between measurement issues and replicability.

@@

<!-- altering latex defaults to get better figure and table placement -->
\renewcommand{\arraystretch}{0.7} <!-- reducing the line spacing within tables -->
\renewcommand{\topfraction}{.85} <!-- max fraction of page for floats at top -->
\renewcommand{\bottomfraction}{.7} <!-- max fraction of page for floats at bottom -->
\renewcommand{\textfraction}{.15} <!-- min fraction of page for text -->
\renewcommand{\floatpagefraction}{.66} <!-- min fraction of page that should have floats -->
\setcounter{topnumber}{3} <!-- max number of floats at top of page -->
\setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page -->
\setcounter{totalnumber}{4} <!-- max number of floats on a page -->
<!-- remember to use [htp] or [htpb] for placement -->

@@

# Introduction 
For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims. Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability]. In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating]. Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study. They found however, that in many instances the results did no match those of the original studies. This lack of replicability of psychological findings illustrated that psychology was facing a so-called 'replication crisis' [@hughes2018psychology; @giner2019crisis].

@@

This thesis aims to investigate the influence of measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects. One goal is to expand the research by [@stanley2014expectations] with a practical example. Whereas they obtained their findings using a simulation study, this thesis intended to investigate the scope of their findings in practice. QMPs in the context of replication research were already investigated by [@flake2022construct]. However, the investigations remained mostly descriptive. This thesis aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by investigating the relation between QMP and replicability.

@@

As a first step it is worth investigating what the state of measurement error is in original and psychological research, in order to assess the scope of @stanley2014expectations's findings in practice. Thus, this thesis will investigate the following:

@@

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. An example of the standardising impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved]. Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure. Heterogeneity is yet another proposed explanation for failed replications. This concern even prompted a Many Labs centred around the testing of heterogeneity in replications [@klein2018many]. However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects amongst replications. These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this thesis analyzed.

@@

This thesis investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings. In particular, this thesis extends research by @stanley2014expectations on the relationship between reliability and replicability, by using data from real life replication projects.

@@

@flake2022construct descriptively investigated QMPs within the reproducibility project psychology [@osc2015estimating]. This thesis seeks to conceptually replicate some of their findings within the Many Labs replication projects.

@@

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this thesis' OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text. This manuscript was generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and XXX data are available at <https://github.com/CasGoos/measurement_and_replication.git>.

@@

The data used for the analyses in this thesis consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 did not contain contain data suitable for this project. The replication made use of videos and eye-tracking as measures, which does not match this thesis' focus on scale and item measures.

@@

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. The specific data was extracted from the replication datasets for each relevant measure. The measure had to consist of multiple scalar items to be considered relevant for the related analyses. Single item measures were not usable for the analyses on score reliability [@wanous1996estimating] as they do not translate directly to the findings of @stanley2014expectations, which this thesis is following up on.

@@

```{r Cleaning Replication Datasets Data, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
### ML 1
# 1.3
data_1.3_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[22:29])
colnames(data_1.3_clean)[1] <- "g"
# 1.10
data_1.10_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[108:115])
colnames(data_1.10_clean)[1] <- "g"
# 1.11
data_1.11_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[73:76])
colnames(data_1.11_clean)[1] <- "g"
# 1.12.1
# not found
# 1.12.3
data_1.12.3.1_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[54:59])
colnames(data_1.12.3.1_clean)[1] <- "g"
data_1.12.3.2_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[60:65])
colnames(data_1.12.3.2_clean)[1] <- "g"

@@

```{r Cleaning Coded Data, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
# Selecting the relevant rows and columns for the data
coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
coded_data_vignette_raw <- coded_data_vignette_raw[3:160, 2]

@@

[^1]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information. The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this thesis <https://osf.io/gft46/%7D>

@@

The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols. Then using the structured coding protocol (made using Qualtrics) available on the OSF page for this thesis (<https://osf.io/9r8yt/>), each measure of a unique variable was coded on measurement reporting and reported reliability.

@@

After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent. As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more favourable judgement of QMPs. These changes included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting. The revision of the coding protocol happened after all the data were coded using the initial protocol. As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this thesis' OSF page: <https://osf.io/9r8yt/>. Both raw and processed formats are present.

@@

Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success. Replication success was based on the test of the main effect of a study. However, the unit of measurement for the data in this thesis was a measure of a unique variable, not an effect. Fortunately, since only primary measures were included in the data, each measured a variable of the main effect, and as a result the measure remains related to the test of the main effect. Replication was based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report. An effect was considered replicated if the meta-analytic p-value was lower than .05, and in the same direction as the original effect. In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.

@@

Two of the qualitative items have an equivalent in the coding key of @flake2022construct. Eleven out of twenty of the quantitative coding variables have an equivalent in @flake2022construct. Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this thesis as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct. Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the aims of this thesis.

@@

```{r Check for Reliability and Validity Testability, include = FALSE, warning = FALSE}
## Checking the measures to recalculate the reliability and factor analysis for.
## The question: "Are they psychometrics scales or not?", is key here.
View(coded_data_replications)

@@

```{r Final Preparation of Data, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
### this code prepares the various pieces of data to be ready to use for the 
### analyses.
## confirmatory analyses
# for hypothesis 4
data_h4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
# for hypothesis 5
data_h5 <- data_prep_H5(coded_data_replications)
# for hypothesis 6
data_h6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)

@@

Every hypothesis test in this thesis used an alpha significance cutoff of .05. No correction for multiple testing was applied, to avoid inflating type II error rate. The generally small sample size and consequently low power of these analyses meant that a smaller alpha would increase the number of false negatives. On top of that, these analyses were considered as exploratory. In this exploratory context, the rate of discovery of any potential true effects was given more value relative to decreasing any false positives compared to typical confirmatory research. That as a consequence obtaining false positives was more likely has been accepted, as false negatives were deemed more harmful to this study's aims.

@@

```{r Hypothesis 1 Model, include = FALSE}
# first some descriptives of reliability reporting
# Measurement type per original and replication:
H1_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)

@@

```{=tex}
\begin{align}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) (\#eq:level1H2) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) (\#eq:level2H2) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij} (\#eq:mixedH2)
\end{align}
```

```{r Hypothesis 2 Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)

@@

```{=tex}
\begin{equation}
ICC = \frac{u_{0j}}{(e_{ij} + u_{0j})} (\#eq:ICC)
\end{equation}
```

A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.

```{r ICC calculations, include = FALSE}
# alpha
within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2

@@

```{=tex}
\begin{equation}
f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i} (\#eq:H3Main)
\end{equation}
```

Where:

```{=tex}
\begin{equation}
f(.) = log\frac{p_{replicated}}{1 - p_{replicated}} (\#eq:LogitLink)
\end{equation}
```

```{r Hypothesis 3 Main Test, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- apa_print(glm(formula = replication ~ 1 + alpha, 
                                      family = binomial(), data = data_h3_avg))

@@

```{r Hypothesis 3 Multilevel Model Sensitivity Analyses, include = FALSE}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h3_multiple))

@@

The reported analyses were primarily based on the revised set of QMP data. The results using the original QMP data are mentioned when the results led to different conclusions. The analysis code for both the original and revised QMP data are available in the R script on both the OSF page (<https://osf.io/9r8yt/>) and github page (<https://github.com/CasGoos/measurement_and_replication.git>) of this article.

@@

```{=tex}
\begin{equation}
g(.) = (0, 1) \mapsto \mathbb{R} (\#eq:BetaLink)
\end{equation}
```

All of these models assume that the QMPs are the same across each replication set. The reason being that only one protocol was analysed per replication set, and several of the questions regarding QMPs focus solely on the reporting of relevant measurement information. This assumption was deemed likely, since each replication within a set was based on the same protocol. Furthermore, the goal of these protocols is to ensure that the measurement practices are equal across the different replication studies of the same original effect.

@@

```{=tex}
\begin{equation}
g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i} (\#eq:H4Main)
\end{equation}
```

```{r Hypothesis 4 Model, include = FALSE}
## Hypothesis 4 beta regression model
# running the model with none revised QMP ratio's
H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)

@@

```{=tex}
\begin{equation}
g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5Main)
\end{equation}
```

Where $replicated_{i}$ is a dummy coded variable, which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise. Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.

```{r Hypothesis 5 Model, include = FALSE}
## Hypothesis 4 beta regression model
H5_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)

@@

```{=tex}
\begin{equation}
g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i} (\#eq:H6Main)
\end{equation}
```

```{r Hypothesis 6 Model, include = FALSE}
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

@@

```{r Hypotheses 5 & 6 Sensitivity Analyses, include = FALSE}
## Hypothesis 5 sensitivity test using a random intercept Guassian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

@@

```{r Hypothesis 6 Associations, include = FALSE}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (original QMP coding)
Results_H6_between <- Associations_H6(data_h6)

@@

```{r Unidimensionality Exploratory Analysis, include = FALSE}
extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
                            data_1.12.3.2_clean, data_2.10.1_clean,
                            data_2.12.1_clean, data_2.12.2_clean, 
                            data_2.12.3_clean, data_2.15_clean, data_2.20_clean,
                            data_2.23_clean, data_3.2.1.1_clean, 
                            data_3.2.1.2_clean, data_3.7.1_clean, 
                            data_3.7.2_clean, data_3.8.2_clean,
                            data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)

@@

# print the table in apa formatting
apa_table(
  replication_ratio_table, align = c("l", "r", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated. These have been treated as not replicated within this table and further analyses throughout the thesis"
  , escape = FALSE, placement = "htp", midrules = 4)

@@

This thesis assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects. Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct. These two studies found that sufficient validity evidence and reliability reporting for measures was lacking, even more so for replications than for original studies. The lack of support found for hypothesis 1 shows that this also held for this thesis' sample. In fact, support was found for an effect in the direction opposite to what was hypothesized in the preregistration, as the original articles reported reliability coefficients more often than replication studies.

>>>>

abstract: |
  Recently, the influence of measurement related issues on replicability has received more investigations. 
  In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
  Building on this new line of research, this study assessed these influences in large scale replication projects. 
  Protocols from the Many Labs replication projects, and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures. Reliability did not relate to replicability, and was generally consistent between labs for each measure in the Many Labs projects. 
  The quality of measurement reporting in replication protocols did however relate to replicability.
  Additionally, tentative evidence was found for a relation between quality of measurement reporting in the protocol of a replication and the quality of measurement reporting in its related original study.
  Recommendations are given for researchers and replicators in order to improve measurement practices in replication, and ward its negative impact on replicability. 
  Additionally, directions are given for future research investigating the relationship between measurement issues and replicability.

@@

<!-- altering latex defaults to get better figure and table placement -->

\renewcommand{\arraystretch}{0.7}

<!-- reducing the line spacing within tables -->

\renewcommand{\topfraction}{.85}

<!-- max fraction of page for floats at top -->

\renewcommand{\bottomfraction}{.7}

<!-- max fraction of page for floats at bottom -->

\renewcommand{\textfraction}{.15}

<!-- min fraction of page for text -->

\renewcommand{\floatpagefraction}{.66}

<!-- min fraction of page that should have floats -->

\setcounter{topnumber}{3} <!-- max number of floats at top of page --> \setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page --> \setcounter{totalnumber}{4} <!-- max number of floats on a page --> <!-- remember to use [htp] or [htpb] for placement -->

@@

# Introduction

For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims. Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability]. In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating]. Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study. They found however, that in many instances the results did no match those of the original studies. This lack of replicability of psychological findings illustrated that psychology was facing a so-called 'replication crisis' [@hughes2018psychology; @giner2019crisis].

@@

This study aims to investigate the influence of measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects. One goal is to expand the research by [@stanley2014expectations] with a practical example. Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings in practice. QMPs in the context of replication research were already investigated by [@flake2022construct]. However, the investigations remained mostly descriptive. This study aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by investigating the relation between QMP and replicability.

@@

As a first step it is worth investigating what the state of measurement error is in original and psychological research, in order to assess the scope of @stanley2014expectations's findings in practice. Thus, this study investigated the following:

@@

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. An example of the standardising impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved]. Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure. Heterogeneity is yet another proposed explanation for failed replications. This concern even prompted a Many Labs centred around the testing of heterogeneity in replications [@klein2018many]. However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects amongst replications. These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.

@@

This study investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings. In particular, this study extends research by @stanley2014expectations on the relationship between reliability and replicability, by using data from real life replication projects.

@@

@flake2022construct descriptively investigated QMPs within the reproducibility project psychology [@osc2015estimating]. This study seeks to conceptually replicate some of their findings within the Many Labs replication projects.

@@

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this article's OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text. This manuscript was generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication.git>.

@@

The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 did not contain contain data suitable for this project. The replication made use of videos and eye-tracking as measures, which does not match this study's focus on scale and item measures.

@@

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. The specific data was extracted from the replication datasets for each relevant measure. The measure had to consist of multiple scalar items to be considered relevant for the related analyses. Single item measures were not usable for the analyses on score reliability [@wanous1996estimating] as they do not translate directly to the findings of @stanley2014expectations, which this study is following up on.

@@

```{r CleaningReplicationDatasetsData, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
### ML 1
# 1.3
data_1.3_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[22:29])
colnames(data_1.3_clean)[1] <- "g"
# 1.10
data_1.10_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[108:115])
colnames(data_1.10_clean)[1] <- "g"
# 1.11
data_1.11_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[73:76])
colnames(data_1.11_clean)[1] <- "g"
# 1.12.1
# not found
# 1.12.3
data_1.12.3.1_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[54:59])
colnames(data_1.12.3.1_clean)[1] <- "g"
data_1.12.3.2_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[60:65])
colnames(data_1.12.3.2_clean)[1] <- "g"

@@

```{r CleaningCodedData, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
# Selecting the relevant rows and columns for the data
coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
coded_data_vignette_raw <- coded_data_vignette_raw[3:160, 2]

@@

[^1]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information. The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>

@@

The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols. Then using the structured coding protocol (made using Qualtrics) that is available on the OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages of this study, each measure of a unique variable was coded on measurement reporting and reported reliability.

@@

After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent. As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more favourable judgement of QMPs. These changes included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting. The revision of the coding protocol happened after all the data were coded using the initial protocol. As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages. Both raw and processed formats are present.

@@

Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success. Replication success was based on the test of the main effect of a study. However, the unit of measurement for the data in this study was a measure of a unique variable, not an effect. Fortunately, since only primary measures were included in the data, each measured a variable of the main effect, and as a result the measure remains related to the test of the main effect. Replication was based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report. An effect was considered replicated if the meta-analytic p-value was lower than .05, and in the same direction as the original effect. In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.

@@

Two of the qualitative items have an equivalent in the coding key of @flake2022construct. Eleven out of twenty of the quantitative coding variables have an equivalent in @flake2022construct. Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct. Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the aims of this study.

@@

```{r ReliabilityValidityTestabilityCheck, include = FALSE, warning = FALSE}
## Checking the measures to recalculate the reliability and factor analysis for.
## The question: "Are they psychometrics scales or not?", is key here.
View(coded_data_replications)

@@

```{r FinalPreparationData, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
### this code prepares the various pieces of data to be ready to use for the 
### analyses.
## confirmatory analyses
# for hypothesis 4
data_h4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
# for hypothesis 5
data_h5 <- data_prep_H5(coded_data_replications)
# for hypothesis 6
data_h6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)

@@

Every hypothesis test in this study used an alpha significance cutoff of .05. No correction for multiple testing was applied, to avoid inflating type II error rate. The generally small sample size and consequently low power of these analyses meant that a smaller alpha would increase the number of false negatives. On top of that, these analyses were considered as exploratory. In this exploratory context, the rate of discovery of any potential true effects was given more value relative to decreasing any false positives compared to typical confirmatory research. That as a consequence obtaining false positives was more likely has been accepted, as false negatives were deemed more harmful to this study's aims.

@@

```{r Hypothesis1Model, include = FALSE}
# first some descriptives of reliability reporting
# Measurement type per original and replication:
H1_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)

@@

```{=tex}
\begin{align}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) (\#eq:level1H2) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) (\#eq:level2H2) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij} (\#eq:mixedH2)
\end{align}
```
```{r Hypothesis2Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)

@@

```{=tex}
\begin{equation}
ICC = \frac{u_{0j}}{(e_{ij} + u_{0j})} (\#eq:ICC)
\end{equation}
```
A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.

```{r ICCCalculations, include = FALSE}
# alpha
within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2

@@

```{=tex}
\begin{equation}
f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i} (\#eq:H3Main)
\end{equation}
```
Where:

```{=tex}
\begin{equation}
f(.) = log\frac{p_{replicated}}{1 - p_{replicated}} (\#eq:LogitLink)
\end{equation}
```
```{r Hypothesis3MainTest, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- apa_print(glm(formula = replication ~ 1 + alpha, 
                                      family = binomial(), data = data_h3_avg))

@@

```{r Hypothesis3MultilevelModelSensitivityAnalyses, include = FALSE}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h3_multiple))

@@

The reported analyses were primarily based on the revised set of QMP data. The results using the original QMP data are mentioned when the results led to different conclusions. The analysis code for both the original and revised QMP data are available in the R script on both the OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages of this article.

@@

```{=tex}
\begin{equation}
g(.) = (0, 1) \mapsto \mathbb{R} (\#eq:BetaLink)
\end{equation}
```
All of these models assume that the QMPs are the same across each replication set. The reason being that only one protocol was analysed per replication set, and several of the questions regarding QMPs focus solely on the reporting of relevant measurement information. This assumption was deemed likely, since each replication within a set was based on the same protocol. Furthermore, the goal of these protocols is to ensure that the measurement practices are equal across the different replication studies of the same original effect.

@@

```{=tex}
\begin{equation}
g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i} (\#eq:H4Main)
\end{equation}
```
```{r Hypothesis4Model, include = FALSE}
## Hypothesis 4 beta regression model
# running the model with none revised QMP ratio's
H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)

@@

```{=tex}
\begin{equation}
g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5Main)
\end{equation}
```
Where $replicated_{i}$ is a dummy coded variable, which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise. Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.

```{r Hypothesis5Model, include = FALSE}
## Hypothesis 5 beta regression model
H5_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)

@@

```{=tex}
\begin{equation}
g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i} (\#eq:H6Main)
\end{equation}
```
```{r Hypothesis6Model, include = FALSE}
## Hypothesis 6 beta regression model
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

@@

```{r Hypotheses5&6SensitivityAnalyses, include = FALSE}
## Hypothesis 5 sensitivity test using a random intercept Guassian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

@@

```{r Hypothesis6Associations, include = FALSE}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (original QMP coding)
Results_H6_between <- Associations_H6(data_h6)

@@

```{r UnidimensionalityExploratoryAnalysis, include = FALSE}
extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
                            data_1.12.3.2_clean, data_2.10.1_clean,
                            data_2.12.1_clean, data_2.12.2_clean, 
                            data_2.12.3_clean, data_2.15_clean, data_2.20_clean,
                            data_2.23_clean, data_3.2.1.1_clean, 
                            data_3.2.1.2_clean, data_3.7.1_clean, 
                            data_3.7.2_clean, data_3.8.2_clean,
                            data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)

@@

# print the table in apa formatting
apa_table(
  replication_ratio_table, align = c("l", "r", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated. These have been treated as not replicated within this table and further analyses throughout the article"
  , escape = FALSE, placement = "htp", midrules = 4)

@@

This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects. Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct. These two studies found that sufficient validity evidence and reliability reporting for measures was lacking, even more so for replications than for original studies. The lack of support found for hypothesis 1 shows that this also held for this study's sample. In fact, support was found for an effect in the direction opposite to what was hypothesized in the preregistration, as the original articles reported reliability coefficients more often than replication studies.
